Variational Monte Carlo on bosonic systems

### 2018-01-22 project_1/article/article.tex
Add description of the simple case
	This is for the local energy when we have a non-interacting
	harmonic oscillator.

>>>>

        \subsubsection{Non-interacting harmonic oscillator}
            We start by finding an analytical expression for $a = 0$ and $\beta
            = 1$, i.e., a non-interaction harmonic oscillator given by the
            wavefunction
            \begin{align}
                \bra{\vf{r}}\ket{\Psi_T}
                = \prod_i^N \exp\bigl[
                    -\alpha |\vf{r}_i|^2
                \bigr],
            \end{align}
            where $|\vf{r}_i| = r_i$. As $a = 0$ the interaction term,
            $w(\vf{r}_i, \vf{r}_j)$, vanishes and the Hamiltonian is given by
            (in the spherical case)
            \begin{align}
                H &= \sum_i^N h(\vf{r}_i)
                = \sum_i^N \Bigl(
                    -\frac{\hbar^2}{2m}\nabla_i^2
                    + \half m \omega^2 r_i^2.
                \Bigr)
            \end{align}
